Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-14 manuscript/draftcssa19.tex
section 2 completed

%The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state. An agent's state includes its current amount of wealth and which proto (if any) it is a member of. Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph. Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.

@@

% cite Bootstrap?
%We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).  Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.

>>>>

The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state. An agent's state includes its current amount of wealth and which proto (if any) it is a member of. Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph. Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.

@@

% cite Bootstrap?
We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).  Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
